A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-10 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Singular Value Decomposition, SVD\sep Upscaling\sep Model Order Reduction, MOD \sep  Principal Component Spaces \sep Permeability field
\end{keyword}

>>>>

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
Singular Value Decomposition (SVD)\sep Upscaling\sep Model Order Reduction (MOR) \sep  Principal Component Spaces \sep Permeability field
\end{keyword}
